A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-09-28 sections/methodology/main.tex
Minor change in some of the mathematics
Write Backwards Induction subsection

Similarly, the entries of the routing matrix are defined by equation 
(\ref{eq:obj_distributor}):
\begin{equation*}
    p_A, p_B \quad s.t. \quad \alpha P(L_A) + (1 - \alpha) B_A = \alpha P(L_B) 
    + (1 - \alpha) B_B \tag{\ref{eq:obj_distributor} revisited}
\end{equation*}

@@

\begin{equation}\label{eq:routing_matrix}
    R_A = 
    \begin{pmatrix}
        (p_{1,1}^A, p_{1,1}^B) & (p_{1,2}^A, p_{1,2}^B) & \dots & 
        (p_{1,N_B}^A, p_{1,N_B}^B) \\
        (p_{2,1}^A, p_{2,1}^B) & (p_{2,2}^A, p_{2,2}^B) & \dots & 
        (p_{2,N_B}^A, p_{2,N_B}^B) \\
        \vdots & \vdots & \ddots & \vdots \\
        (p_{N_A,1}^A, p_{N_A,1}^B) & (p_{N_A,2}^A, p_{N_A,2}^B) & \dots & 
        (p_{N_A,N_B}^A, p_{N_A,N_B}^B) \\
    \end{pmatrix}
\end{equation}

@@

>>>>

Similarly, the entries of the routing matrix are defined by equation 
(\ref{eq:obj_distributor}):
% TODO: Make sure this is defined PROPERLY and CONSISTENTLY in model_overview section or here in model_overview section or here
\begin{equation*}
    (p_A, p_B) \quad s.t. \quad 
    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
    \tag{\ref{eq:obj_distributor} revisited}
\end{equation*}

@@

\begin{equation}\label{eq:routing_matrix}
    R = 
    \begin{pmatrix}
        (p_{1,1}^A, p_{1,1}^B) & (p_{1,2}^A, p_{1,2}^B) & \dots & 
        (p_{1,N_B}^A, p_{1,N_B}^B) \\
        (p_{2,1}^A, p_{2,1}^B) & (p_{2,2}^A, p_{2,2}^B) & \dots & 
        (p_{2,N_B}^A, p_{2,N_B}^B) \\
        \vdots & \vdots & \ddots & \vdots \\
        (p_{N_A,1}^A, p_{N_A,1}^B) & (p_{N_A,2}^A, p_{N_A,2}^B) & \dots & 
        (p_{N_A,N_B}^A, p_{N_A,N_B}^B) \\
    \end{pmatrix}
\end{equation}

Note that since \(p_{i,j}^A + p_{i,j}^B = 1\) the routing matrix needs only to
store one of the two values; either \(p_{i,j}^A\) or \(p_{i,j}^B\).
Thus, the routing matrix \(R\) can be simplified to:

\begin{equation}\label{eq:routing_matrix_simplified}
    R = 
    \begin{pmatrix}
        p_{1,1}^A & p_{1,2}^A & \dots & p_{1,N_B}^A \\
        p_{2,1}^A & p_{2,2}^A & \dots & p_{2,N_B}^A \\
        \vdots & \vdots & \ddots & \vdots \\
        p_{N_A,1}^A & p_{N_A,2}^A & \dots & p_{N_A,N_B}^A \\
    \end{pmatrix}
\end{equation}

@@

In order to populate the payoff matrices and the routing matrix the method
of backwards induction is used.
Consider figure \ref{fig:imperfect-info-game} and the flow of the game that was
described (i.e. \(Q_A, Q_B \rightarrow D\)).
Due to the fact that the payoff matrices \(A\) and \(B\) depend on the routing 
matrix \(R\) the entries of the matrices are calculated in a backwards way 
(\(D \rightarrow Q_A, Q_B\)). 
Thus for every pair of strategies \(T_A, T_B\), the proportion of individuals 
that are to be transported to each queueing system is calculated first.

Consider a game where the capacities of the two systems are \(N_A = 4\) and 
\(N_B = 3\).
The strategy space of players \(Q_A\) and \(Q_B\) would then be 
\(T_A = \{1, 2, 3, 4\}\) and \(T_B = \{1, 2, 3\}\) respectively.
Now, starting from an arbitrary starting point of \(T_A=1\) and \(T_B=1\), the
corresponding entry of the routing matrix the routing matrix can be calculated.
Using equation \ref{eq:obj_distributor} for \(T_A=1\) and \(T_B=1\):

\begin{equation*}
    (p_A, p_B) \quad s.t. \quad 
    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
\end{equation*}

The above equation can be solved by using Brent's bisection algorithm.
% TODO: Cite Brent's algorithm
The calculated value of \(p_A\) corresponds to the entry on the first row and 
first column of the routing matrix:

\begin{equation}\label{eq:routing_matrix_1_1}
    R = 
    \begin{pmatrix}
        p_{1,1}^A & - & - \\
        - & - & - \\
        - & - & - \\
        - & - & - \\
    \end{pmatrix}
\end{equation}

In fact all remaining values of the routing matrix can be calculated by
solving \(N \times M\) similar equations using Brent's bisection algorithm.
Therefore, having calculated the entire routing matrix the payoff matrices can
be calculated.
Consider once again the case of \(T_A=1, T_B=1\).

% TODO: Make sure this is defined PROPERLY and CONSISTENTLY in model_overview section or here
\begin{equation*}
    U_{1, 1}^A = \quad 1 -\left( 
        \hat{P} - P(W_A < R) 
    \right)^2,
    \quad
    U_{1, 1}^B = \quad 1 -\left( 
        \hat{P} - P(W_B < R) 
    \right)^2 \tag{\ref{eq:payoff-entry} revisited}
\end{equation*}

These are the utilities of players \(A\) and \(B\) when both players choose a
strategy of \(T = 1\).
% TODO: Change R everywhere to t
Here \(R\) is the predefined waiting time target to be met by a percentage of 
individuals \( \hat{P} \) and \(P(W_i < R)\) is properly defined in section
\ref{sec:proportion_within_target}.

\begin{equation}\label{eq:payoff_matrices_1_1}
    A = 
    \begin{pmatrix}
        U_{1, 1}^A & - & - \\
        - & - & - \\
        - & - & - \\
        - & - & - \\
    \end{pmatrix}, \quad
    B = 
    \begin{pmatrix}
        U_{1, 1}^B & - & - \\
        - & - & - \\
        - & - & - \\
        - & - & - \\
    \end{pmatrix}
\end{equation}

Similar to the routing matrix, the above procedure can be repeated for all 
possible values of \(T_A\) and \(T_B\) to populate all entries of the payoff 
matrices.
